
\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.5in,right=0.5in,top=0.4in,bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{calc}
\usepackage{color}
\usepackage{xcolor}
% Define custom section styles
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove page numbers
\pagestyle{empty}

\definecolor{bg}{HTML}{F0F0C9}
\definecolor{fg}{HTML}{32373B}

\begin{document}

\pagecolor{bg}

\begin{center}
    \textbf{\LARGE ETHAN 
    POLLACK} \\
    \href{tel:(818) 398-8996}{(818) 398-8996} \quad
    \href{mailto:epollack31@gmail.com}{epollack31@gmail.com} \quad
    \href{https://epoll31.github.io}{epoll31.github.io} \quad
    \href{https://github.com/epoll31}{github.com/epoll31}
\end{center}

\noindent A highly motivated, experienced, and passionate developer seeking to deliver high quality work product within a leading-edge environment. An “outside the box” problem solver with strong communication skills passionate about programming and robotics, looking for an environment that will provide ongoing challenges, growth, and learning opportunities.

\section*{Education}
\subsection*{Worcester Polytechnic Institute} Bachelor of Science in Computer Science | GPA: 3.77 \textit{(Graduated Dec. 2023)}\\
Focus Areas: Programming Language Design, Software Development Techniques, Agile Methodologies, Game Dev.
\subsubsection*{Significant Accomplishments:}
    \begin{itemize}
        \item \textbf{Major Qualifying Project:} June 2023 - October 2023\\
        Authored a detailed research paper comparing various industry standard databases from a pedagogical perspective for use as teaching materials at WPI. Used various database IDEs and languages including OracleSQL, MySQL, and PostgreSQL.
        \item \textbf{Interactive Qualifying Project:} October 2022 - February 2023\\
        Developed an interactive game for a local Boys and Girls Club as a key deliverable within a research project bringing together members from various majors and interdisciplinary areas. The game promotes learning about the Nitrogen Life Cycle. Computer Vision was used to scan barcodes and display 3D graphics in Augmented Reality on the player’s device.
        \item \textbf{Software Engineering Project:} March 2022 - May 2022\\
        Implemented an application for employees to request hospital equipment. Utilized Agile Methodologies including daily scrums as well as various industry standard programming tools such as OracleSQL, Java, JetBrains.
    \end{itemize}


% \subsection*{Calabasas High School}
% Graduated June 2020 
% \hspace{2em}
% Scores: GPA 4.45
% \hspace{2em}
% AP Computer Science: 5 \\\\
% Honors / Awards:
% \begin{itemize}
%     \item California Scholarship Federation
%     \item Graduated as Salutatorian
% \end{itemize}
% Athletics: Tennis Team - 4 years \& varsity captain senior year

\section*{Work Experience}
\subsection*{Software Development (Paid Internship), Epic Systems} May 2023 - August 2023 \\
Designed and developed a key component in the “MyChart” application using React, JavaScript, TypeScript, HTML, and CSS. Used proprietary knowledge from previous tenure to deliver bug-free code meeting Epic standards. Exceeded expectations by delivering results ahead of schedule.

\subsection*{Project Manager \& Lead Developer, Build-It-Yourself} October 2022 - May 2023 \\
Led team to develop and implement a website enabling children to share their art work with others. Taught programming classes to students.  

\subsection*{Software Development (Paid Internship), Epic Systems}
May 2022 - August 2022 \\
Developed a project that improved “EpicCare Link” using the React framework, JavaScript, TypeScript, HTML, CSS, and Visual Basic. Gained experience working on production software within a large team structure as well as a large code base for mission critical Electronic Health Record (EHR) software utilized by thousands of healthcare organizations.

\subsection*{Programming Instructor, Great Minds Robotics}
June 2019 - July 2020 \\
Taught advanced programming classes. Mentored junior robotics team members. Leveraged knowledge from past experience. Focused on middle school to college students.

% \subsection*{Camp Counselor, Skylake Yosemite Camp}
% June 2021- August 2021 \\
% Took care of kids aged 7 to 14 all day.

\section*{Programming Languages | Technical Skills}
\begin{itemize}
    \item \textbf{Proficient in:} Python, C\#, Java, C++, CMake, Swift, HTML, CSS, TypeScript, Rust, SQL, Lua, Bash, etc
    \item \textbf{Frameworks, IDE's, and other tools:} Git, GitHub, Jira, React, Unity, Visual Studio Enterprise, Visual Studio Code, the JetBrains' ecosystem, Next.js, NPM, Cargo, VCPKG, Processing, NeoVim, Photoshop, Illustrator, OpenCV, CAD Softwares, 3D Graphics, and 3D for HoloLens in Unity, 2d Graphics, and more
\end{itemize}

\section*{Robotics \& Programming Experience}
\subsection*{World Robotics Olympiad Competitions}
2018 \& 2019 \\
Lead builder and secondary coder on a 3-person team. Responsible for robot design and build. Partnered in developing overall strategy. Won numerous awards including Best Robot Design. Competed in the World’s event in Hungary.

\subsection*{VEX IQ Competitions}
2015 \& 2017 \\
Lead Builder and secondary coder on a 2-person team. Competed at multiple events throughout the year - placing first in California, first in the U.S., and 9th at the World’s Competition (out of 200 teams).

% \section*{Volunteer Experience}
% \subsection*{National Honors Society Tutor, Las Virgenes School District}
% Oct 2018 - May 2020 \\
% Tutor high school students in math, computer science \& statistics.

% \subsection*{Technology Support, Calabasas Senior Center}
% July 2018 - May 2020 \\
% Assist senior citizens with computer, smartphone, and technology related issues.

% \subsection*{Computer Science Tutor, Calabasas High School}
% September 2017 - June 2020 \\
% Assisted classmates with Computer Science curriculum after school and on weekends.

\end{document}

